Growing up with Nell: A Narrative Interface for Literacy

### 2012-03-08 paper.tex
Rough in 'Personalization' section.

% not always a story -- kid can draw on their own and return to the
% story; Nell will observe the free play and offer suggestions.
\subsection{Personal}
% customization, renaming characters

Kids love to personalize stuff \textbf{[CITATION NEEDED]}.

\subsection{Direct interaction}
% handwriting as UI?
% motor skills
% photo of XO-3?
\subsection{Growable (``no ceiling'')}
% it has a ``low floor and no ceiling'' to allow a child to master more
% and more of the system as she grows.

@@

>>>>

% not always a story -- kid can draw on their own and return to the
% story; Nell will observe the free play and offer suggestions.
\subsection{Personalization}
% customization, renaming characters

Children often decorate their belongings, and the
child owning a Nell system is encouraged to personalize it.
Superficially, colors can be changed and characters can be renamed and
dressed up.  But Nell also supports story personalization at a deeper
level.

Choices the child has made are stored in an \textit{Avatar Services}
module, accessible to all story modules and activities.  Past choices
can thus influence the future direction of a story.  Story module
alternates are supported to allow learning material to presented in
different ways for different learners. Further, the record of a
child's experiences with Nell are recorded in a \textit{Journal},
which can be edited and customized by the user.  Careful arrangement
of sections of the Journal can become a Portfolio \textbf{cite here}.
The journal also allows undo/redo \textbf{XXXX}.

In the future, we expect to allow further personalization via deep
recombination of story elements.  Lebowitz \textbf{PLANNING} and Riedl
\textbf{PLANNING} show how a planner can be used to recombine story
modules.  We expect to be less ambitious then previous work: instead
of attempting to generate thousands of stories from tens of templates,
we expect to modestly adapt from hundreds of story modules created
in a decentralized manner by teachers.

\subsection{Direct interaction}
% constructionist?
% handwriting as UI?
% motor skills
% photo of XO-3?

\subsection{Growable (``no ceiling'')}
% it has a ``low floor and no ceiling'' to allow a child to master more
% and more of the system as she grows.

@@

%%  LocalWords:  personalization
